\chapter{Introduction}\label{introduction}
The internet is a growing source of revenue and information. Being able to analyze this collection of data is very useful. Most website analysis is done by looking at the content of a website, but not at the web page layout itself. However being able to analyze and compare web page layouts might be more worthwhile then we think. We could for example remove redundant backups of websites by looking if their layout has changed or use clustering to group different websites with similar designs.
\\ To be able to use modern analysis tools, we have to be able to quantify distance between two elements. If we are able to calculate the distance between different web pages we can see which web pages are similar and which ones differ the most.
\\ A simple solution would be retrieving certain attributes about the web page's design, for example most used color, and then using vector distance as a metric. However the outcome is entirely dependent on the attributes that where chosen, and no clear guidelines on constructing such guidelines exist. Unfortunately, when quantifying distance over large and complex data elements, it becomes more difficult to find a purely objective metric. Because, while we would still be able to say whether two web pages differ, being able to say what web page is more different becomes more of a subjective decision.\\
In our research we use an adapted version of the tree edit distance algorithm, while it is not known if this objective approach of measuring the distance between layouts is consistent with human judgment, we assume the original algorithm is sufficiently close to be meaningful, and we will evaluate our own adaptation.\\
However to do this, we have to find a way of translating web pages into data trees, so that we can then use our tree edit distance to analyze our data.\\
\section{Focus of this research}
Our research focuses on the following two questions:
\begin{itemize}
\item Is it possible to gain useful information about websites, while only analyzing the web page layout?
\item Is tree edit distance a good proxy for comparing web page layouts?
\end{itemize}
By answering these, we hope to be able to show that analyzing web page layouts is possible and worth the effort.